### 2016-10-31 paper/evaluation.tex
some text related to time distribution

To evaluate the distribution of execution time, we collected from the
test report (\ie, Surefire XML file) the elapsed time to execute
each test case and \Fix{...to be continued...}.

>>>>

To evaluate the distribution of execution time, we calculated the cost
from 90\% of test cases ordered by execution time and compared the
resulting value to the total time.  We collected the elapsed time from
test cases for each generated report. Maven Surefire generates an XML
report with execution information (\eg, number of skipped tests and
elapsed time) per test suite \Jbc{Should I use the previous sentence
as a footnote or should I delete it?}. We noticed that some test
cases reported an elapsed time of zero: since the reported time is in
milliseconds, some tests may execute in a shorter time.
